---
title: "Batch geocoding with opencage"
date: '`r Sys.Date()`'
author: Daniel Possenriede
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  error = TRUE, # don't stop at errors
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv(LANGUAGE = "en") # error messages in English
```
... and some other ideas & questions regarding opencage

# Motivation

I'd like to use `opencage` for batch (forward) geocoding, usually a few hundred addresses at the time. Most of the time the addresses are in a dataframe together with other information (so that's why I am using the `places_df`).


```{r lib_data}
suppressPackageStartupMessages(library(tidyverse))
library(opencage)

elphi <- "Elbphilharmonie, Hamburg"
sherlock <- "Baker Street 221b, London"
triumph <- "Arc de Triomphe de l’Etoile, Paris"

places <- 
  c(elphi, 
    sherlock,
    triumph)

places_df <- data.frame(places, stringsAsFactors = FALSE)

```

`opencage_forward` is not vectorized, so giving it more than one address results in an error

```{r}
opencage_forward(places)
```

(maybe it could provide a better error message?)

But one ["just"](https://github.com/ropensci/opencage/issues/19) needs to use `purrr`. 

# Purrrify

I came up with two different, though similar ways to do this, but there probably is another/better way?

Either `map` `opencage_forward` over the placename column, turn the results into a dataframe and join that dataframe with the original dataframe (you need `add_request` to be `TRUE` for that).

```{r}
oc_places_lst <- purrr::map(places_df[["places"]], opencage_forward, limit = 1)
oc_places_df <- suppressWarnings(purrr::map_df(oc_places_lst, "results"))
oc_places_df <- left_join(places_df, oc_places_df, by = c("places" = "query"))

```
(The `suppressWarning` is due to a lot of warnings about unequal factor levels. Maybe add a `stringsAsFactors = FALSE` to `opencage_parse`?)

Or `mutate` the result from a `map`ed `opencage_forward` into a list column 
```{r}

oc_places_df2 <- 
  places_df %>% 
  mutate(
    oc = purrr::map(.[["places"]], opencage_forward, limit = 1) %>% 
      purrr::map("results")
  )
oc_places_df2 <- suppressWarnings(unnest(oc_places_df2, oc))

```

## Problems with this approach

I find both not very satisfactory, because they are both not very user-friendly IMHO and easily fail with unusual data.

For example if one gets a `NULL` result


```{r null_return}
not_a_place <- "dpprdan"

not_all_places <- c(places, not_a_place)

not_all_places_df <- tibble(not_all_places)

oc_na_places_df2 <- 
  not_all_places_df %>% 
  mutate(
    oc = purrr::map(.[["not_all_places"]], opencage_forward, limit = 1) %>% 
      purrr::map("results")
  )

oc_na_places_df2 <- suppressWarnings(unnest(oc_na_places_df2, oc))


```
There probably is a way for `unnest` to deal with NULL lists, but I am not aware of it. 
`NULL` results do not seem to be a problem with the first method, though. 

There will be unexpected results with the first method if one is not carefull, though, when there are address duplicates in the list.

```{r}
places_dubl <- 
  c(places, elphi)

places_dubl_df <- data.frame(places_dubl, stringsAsFactors = FALSE)

oc_places_dubl_lst <-
  purrr::map(places_dubl_df[["places_dubl"]], opencage_forward, limit = 1)
  
oc_places_dubl_df <-
  suppressWarnings(purrr::map_df(oc_places_dubl_lst, "results"))
oc_places_dubl_df <-
  left_join(
    places_dubl_df,
    oc_places_dubl_df,
    by = c("places_dubl" = "query")
  )
  
nrow(places_dubl_df) == nrow(oc_places_dubl_df)

```

This can be avoided if by doing a `unique(oc_places_dubl_df)` before the `left_join`.

# Some other ideas for improvement(?)

## url-only

For debugging I find an `urlonly` option quite handy. What does the url, the package sends to the API, look like and is it really what I think it is? See e.g. `ggmap::geocode`:

```{r}
ggmap::geocode("1600 pennsylvania avenue, washington dc", urlonly = TRUE)
```

## Better (HTTP) error-handling

HTTP errors result in an R error (as opposed to a warning) and stop the whole function. Now, when a function errors out, e.g. because you loose the internet connection during a batch geocode, all results until then will be lost. I don't know how to fake a shaky internet connection at the moment, so as an example see this with an invalid key. 

```{r}
# catch errors in column
opencage_forward(elphi, key = "not_a_valid_key")

```

It would be better to get a warning (maybe written into a separate column (purrr::possibly or something from the attempt package)) than to get an error.

## Rate-Limiting

`opencage_forward` and `opencage_reverse`are not rate-limited (right?), i.e. there is no limit on how often they call the API per second. However, dependend on the type of [subscription](https://geocoder.opencagedata.com/pricing). opencage (the API) allows between 1 and 15 requests per second. This can become a problem with batch geocoding and even if it does not, it is simply nice to obey the rate limits. So maybe use `ratelimitr` and make the `rate` adjustable via `options()`, e.g. `limit_rate(opencage_get, getOption(OPENCAGE.rate)`). Regarding options, I like the approach of ggmap (v. 2.7), with all ggmap options grouped in a [list](https://github.com/dkahle/ggmap/blob/master/R/zzz.R) that can be [set](https://github.com/dkahle/ggmap/blob/master/R/register_google.R) and [read](https://github.com/dkahle/ggmap/blob/master/R/ggmap_credentials.R) with custom functions.

## Encoding

I thought I had an issue once with non-cp1252 ("latin-1" in R) strings. But apparently this works.

```{r}
palace <- "Дворцовая пл., Санкт-Петербург, Россия"
opencage_forward(palace)
```


## Multiple countrycodes

opencage supports [multiple country codes(https://geocoder.opencagedata.com/api#forward-opt), but `opencage` does not (yet).

```{r countrycodes}
# French territories according to the opencage website
french_territories <- 
  c("fr", "bl", "gf", "gp", "mf", "mq", "nc", "pf", "pm", "re", "tf", "wf", "yt") %>% 
  toupper()

opencage_forward("Arc de Triomphe de l’Etoile, Paris", countrycode = french_territories)

```

