---
title: "Batch geocoding with rmapzen"
date: '`r Sys.Date()`'
author: Daniel Possenriede
output: github_document
---

<!-- bath_geocode_rmapzen.md is generated from bath_geocode_rmapzen.Rmd Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  error = TRUE, # don't stop at errors
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv(LANGUAGE = "en") # error messages in English
```


```{r lib_data}
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(tidyverse))
library(rmapzen)

elphi <- "Elbphilharmonie, Hamburg"
sherlock <- "Baker Street 221b, London"
triumph <- "Arc de Triomphe de l’Etoile, Paris"

places <- 
  c(elphi, 
    sherlock,
    triumph)

places_df <- data.frame(places, stringsAsFactors = FALSE)

```


`mz_search` is the general function for forward geocoding. It creates an `mapzen_geo_list` object (which has it's own `print` method).

```{r}
(mz_search_elphi <- mz_search(elphi))
# saveRDS(mz_search_elphi, here("rmapzen/mz_search_elphi.rds"))

```
The results are relatively "raw", i.e. they have only been parsed by `jsonlite::fromJSON()`.

`mz_geocode` is a dedicated function to geocode an address, utilizing the more general `mz_search` function. It returns a data.frame with a formated address, longitude, latitude and confidence.



```{r}
(mz_geocode_elphi <- mz_geocode(elphi))
# saveRDS(mz_geocode_elphi, here("rmapzen/mz_geocode_elphi.rds"))

```


Both are not vectorized, so this gives an error.

```{r}
mz_geocode(places)

```

Utilizing `purrr::map_df`

```{r}

(mz_bind_places_df <- 
  places_df[["places"]] %>% 
  purrr::map_df(mz_geocode) %>% 
  bind_cols(places_df, .))

```

Or `mutate` the result from a `map`ed `mz_geocode` into a list column 
```{r}

(mz_mutate_places_df <- 
  places_df %>% 
  mutate(codes = map(places, mz_geocode)) %>% 
  unnest(codes))

```

## Problems

### `NULL` results


For example if one gets a `NULL` result


```{r null_return}
not_a_place <- "dpprdan"

not_all_places <- c(not_a_place, places)

not_all_places_df <- tibble(not_all_places)

mz_na_places_df2 <- 
  not_all_places_df %>% 
  mutate(codes = map(places, mz_geocode)) %>% 
  unnest(codes)

```
There probably is a way for `unnest` to deal with NULL lists, but I am not aware of it. 
This does work with the first method. 

### Encoding 

Apparently not a problem

```{r}
palace <- "Дворцовая пл., Санкт-Петербург, Россия"

mz_geocode(palace)

```

### Getting more information

It is not really easy to extract additional information from mz_search result. Compare for example  `ggmap::geocode` output options, `c("latlon", "latlona", "more", "all")`, which returns dataframes with varying information (`"all"` returns a list, though). A option/function that outputs all `feature`s as a data.frame would suffice, though. But there is already an [issue](https://github.com/tarakc02/rmapzen/issues/12) for this.

```{r}
mz_search_elphi[["features"]][[1]]

```


