---
title: "Some Tests of the Opencage Package"
date: '`r Sys.Date()`'
author: Daniel Possenriede (@dpprdan)
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  error = TRUE, # don't stop at errors
  collapse = TRUE,
  comment = "#>"
)
Sys.setenv(LANGUAGE = "en") # error messages in English
```


```{r lib_data}
# devtools::install_github("dpprdan/opencage@output_options")
suppressPackageStartupMessages(library(tidyverse))
library(opencage)

elphi <- "Elbphilharmonie, Hamburg"
sherlock <- "Baker Street 221b, London"
triumph <- "Arc de Triomphe de l’Etoile, Paris"

places <- 
  c(elphi, 
    sherlock,
    triumph)

places_df <- data.frame(places, stringsAsFactors = FALSE) %>% rowid_to_column()

```

# Single placename

## return dataframe, multiple results

```{r}
oc_forward(triumph, output = "df_list") # df_list is default
```

## return list

Output not shown, because output contains API key (in `$request$key`)

```{r eval=FALSE, include=TRUE}
oc_forward(triumph, output = "json_list")
```

## return JSON string

E.g. for use with `jqr`, output not shown.

```{r eval=FALSE, include=TRUE}
oc_forward(triumph, output = "json_list") %>% 
  jsonlite::toJSON()
```

# Multiple results with column binding

## return dataframe, single result

```{r}

places_df %>% 
  mutate(
    oc = oc_forward(places, limit = 1, output = "df_list")) %>% 
  tidyr::unnest(oc) %>% class()
    
```

## return dataframe, multiple results, no_annotations

```{r}

places_df %>% 
  mutate(
    oc = oc_forward(places, output = "df_list", no_annotations = TRUE)) %>% 
  tidyr::unnest(oc)
    
```


## dataframe with R list column with parsed JSON

output not shown

```{r eval=FALSE, include=TRUE}

places_df %>% 
  mutate(
    oc = oc_forward(places, limit = 1, output = "json_list"))
    
```

## input character vector, output dataframe

```{r}
oc_forward(places, limit = 1, output = "df_list") %>% 
  bind_rows()
```


# Source with problems

Duplicates, empty placename, not a real placename (i.e. no result), NA placename.

```{r}
places2 <- 
  c(elphi, 
    sherlock,
    triumph,
    elphi,
    "",
    "dpprdan")

places2_df <- 
  data.frame(places2, stringsAsFactors = FALSE) %>%
  rowid_to_column()

```

```{r}

places2_df %>% 
  mutate(
    oc = oc_forward(places2, output = "df_list", no_annotations = TRUE)) %>% 
  tidyr::unnest(oc)
    
```


# Remaining Problems 

- [ ] countrycode per row not yet possible (need to change vectorisation in `oc_forward()` from `purrr::map` to `purrr::pmap`)
- [ ] `NA_character` as placename (returns results for `placename = "NA"`)
- [ ] `add_query` parameter (use placename directly from R, not via API roundtrip)
- [ ] handle (HTTP) errors while querying: `purrr::safely`?!

